Indexes measures for oak decline severity using phenotypic descriptors

### 2019-07-12 manuscript/manuscript.Rmd
added descriptor adjustment figure
added DI figure
added descriptor contributions figure

```{r figure_1}
source('../code/Figure_1_site_differences.R')

figure1 %>%
  wrap_plots()
```

>>>>

```{r site_differences}
source('../code/site_differences.R')

site_differences %>%
  wrap_plots()
```

```{r descriptor_adjustment,fig.cap='Error bars show ±1SE of the mean.\nDashed red line shows the overall mean.'}
source('../code/descriptor_adjustment.R')

descriptor_adjustment %>%
  wrap_plots()
```

```{r DIspace}
DIspace()
```

```{r}
source('../code/descriptor_contributions.R')
descriptor_contributions %>%
  wrap_plots() + 
  plot_annotation(title = 'Descriptor importance scores from random forest models for relative contributions to\ndecline index measures',caption = 'Gini importance scores averaged across 100 repetitions')
```
